A Survey of Current Exoskeletons and Their Control Architectures and Algorithms\\ (Draft 3.1)

### 2015-09-29 survey.tex
more updates

>>>>

This paper surveys the following exoskeletons in detail:
\begin{itemize}
\item
{\bf BLEEX:} a ``minimal-sensing'' and aggressive model-based control design point.
\item
{\bf HAL:} an EMG controlled exoskeleton.
\item
{\bf XoR:} a hybrid Pneumatic/Electric-motor system.
\item
{\bf Body Extender:} a fully actuated full body exoskeleton.
\item
{\bf HLEE:} uses torque control approach.
\item
{\bf IHMC MAE:} an SEA-based torque controlled exoskeleton.
\item
{\bf MIT Exoskeleton:} an attempt to take advantage of the passive dynamics
of walking.
\item
{\bf Roboknee:} an example of a single-joint exoskeleton.
\end{itemize}

We then list other systems in a variety of categories.

\section{Introduction}
